Predictive modeling with cross validation

### 2017-08-11 model fitting/cross_validation.Rmd
finished recoding category variable

# adding interaction terms
r2_i <- coxph(Surv(time_until_answer, answered) ~ new_category + n_images + new_user + weekday + ampm + device_length + title_questionmark + title_beginwh + capital_text + update + newline_ratio + frequent_tag + contain_answered + contain_unanswered + title_questionmark*title_beginwh + new_user*update + new_user*newline_ratio, data = train1)
AIC(r2_i, k = 2) # 65037.36
summary(r2_i)
```

@@

* separate iPhones/Androids (or group all apple products together?) - use str_detect to find categories with apple/iphone/mac (since there are apple watches in the apparel category)
* keep Mac and PC the same
* group all categories that have less than 100 questions together? 
* group electronics + median player
* group household + appliance
* group car and truck + vehicle

@@

train1 %>%
  group_by(category) %>%
  summarise(median_t = median(time_until_answer), n = n()) %>%
  arrange(median_t)

# recoding category variable
train1$new_category <- as.character(train1$category)
train1$new_category[train1$subcategory == "iPhone"] <- "iPhone"
train1$new_category[train1$new_category == "Phone"] <- "Android/Other OS Phone"
train1$new_category[train1$new_category == "Electronics" | train1$new_category == "Media Player"] <- "Electronics/Media"
train1$new_category[train1$new_category == "Household" | train1$new_category == "Appliance"] <- "Home"
train1$new_category[train1$new_category == "Car and Truck"] <- "Vehicle"

#if there are less than 50 questions in a certain category, group with "Other"
n <- train1 %>%
  group_by(category) %>%
  summarise(n = n())
# fix this (not working correctly)
for (i in nrow(n)) {
  if (n$n[i] < 50) {
    train1$new_category[train1$category == n$category[i]] <- "Other"
  }
}

# model with new_category- AIC dropped 
r2_new <- coxph(Surv(time_until_answer, answered) ~ new_category + n_images + new_user + weekday + ampm + device_length + title_questionmark + title_beginwh + capital_text + update + newline_ratio + frequent_tag + contain_answered + contain_unanswered + title_questionmark*title_beginwh + new_user*update + new_user*newline_ratio, data = train1)
AIC(r2_new, k = 2) # 64743.48
summary(r2_new)
```

```{r}

```

>>>>

# adding interaction terms
r2_i <- coxph(Surv(time_until_answer, answered) ~ category + n_images + new_user + weekday + ampm + device_length + title_questionmark + title_beginwh + capital_text + update + newline_ratio + frequent_tag + contain_answered + contain_unanswered + title_questionmark*title_beginwh + new_user*update + new_user*newline_ratio, data = train1)
AIC(r2_i, k = 2) # 65037.36
summary(r2_i)
```

@@

* group all apple products together (use str_detect to search for Apple, ipad, ipod)
* recode left over Phones to Android/Other Phone
* group household + appliance as "Home"
* group car and truck + vehicle as "Vehicle"
* set a rule: any category with less than 50 questions gets grouped with "Other"

@@

train1 %>%
  filter(category == "Media Player") %>%
  group_by(subcategory) %>%
  summarise(median = median(time_until_answer), n = n(), prop_a = sum(answered)/n)

#===================================================
# recoding category variable
train1$new_category <- as.character(train1$category)

# grouping apple products together
apple_terms <- c("apple", "ipod", "ipad")
train1$apple <- str_detect(str_to_lower(train1$device), pattern = START %R% or1(apple_terms) %R% SPC)
train1$new_category[train1$apple == TRUE | train1$subcategory == "iPhone" | train1$category == "Mac"] <- "Apple Product"

# renaming left over phones 
train1$new_category[train1$new_category == "Phone"] <- "Android/Other Phone"
train1$new_category[train1$new_category == "Appliance" | train1$new_category == "Household"] <- "Home"
train1$new_category[train1$new_category == "Car and Truck" | train1$new_category == "Vehicle"] <- "Vehicle"

# if there are less than 60 questions in a category, group them with other
counts <- train1 %>%
  group_by(new_category) %>%
  summarise(n = n())
for (i in which(counts$n <= 100)) {
  train1$new_category[train1$new_category == counts$new_category[i]] <- "Other"
}

table(train1$new_category)

# model with new_category 
r2_new <- coxph(Surv(time_until_answer, answered) ~ new_category + n_images + new_user + weekday + ampm + device_length + title_questionmark + title_beginwh + capital_text + update + newline_ratio + frequent_tag + contain_answered + contain_unanswered + title_questionmark*title_beginwh + new_user*update + new_user*newline_ratio, data = train1)
AIC(r2_new, k = 2) # 64728.77
summary(r2_new)
```
